Probabilistic Programming

### 2014-04-20 paper/paper.tex
Update paper.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}

@@

  \bibitem{markov} Takis Konstantopoulos {\em Introductory lecture notes on
Markov Chains and Random Walks} Uppsala University, URL = http://www2.math.uu.se/~takis/L/McRw/mcrw.pdf

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}

@@

	\bibitem{markov} Takis Konstantopoulos {\em Introductory lecture notes on
	Markov Chains and Random Walks} Uppsala University, URL = \url{http://www2.math.uu.se/~takis/L/McRw/mcrw.pdf}
